Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
Add additional sentence about precursor decay heat.

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the plots are
chosen to correspond to the peak of the thermal flux in both cases; for the
\gls{ORNL} calculations this is 21.336 cm (8.4 inches) from the core center-line because of
the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the \gls{MSRE} lines extend to lower and
higher z-values than the Moltres lines. Additionally, absorption
in the plena cause deviation of the thermal flux from a sinusoidal shape in the
\gls{MSRE} design case.

@@

Although the qualitative agreement is decent, there are discrepancies between
the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
the hottest channel. The peak graphite temperature is around 14 K larger in the
Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
roughly 20\%. These are not insignificant differences. However, given the
differing nature of the two models--no axial conduction in the \gls{MSRE} model,
2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
Moltres calculation--we believe this variation in quantitative behavior is
acceptable for the purpose of this work, which is to introduce Moltres as a
simulation tool. Trustworthy verification of Moltres results, such as spatial flux
and temperature profiles, will require more detailed experimental measurements
than those available in the \gls{ORNL} technical reports, which contain only
macroscopic data such as steady-state power and heat-exchanger temperature
drops. Additionally, detailed comparison with other modern modeling efforts such
as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
desirable. In that vein, a collaboration is under way with the primary author of
\cite{aufiero_develoment_2014} to try and reproduce calculation results from
OpenFOAM. We hope to publish the results of this comparison in a future work.

>>>>

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the plots are
chosen to correspond to the peak of the thermal flux in both cases; for the
\gls{ORNL} calculations this is 21.336 cm (8.4 inches) from the core center-line because of
the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the \gls{MSRE} lines extend to lower and
higher z-values than the Moltres lines. Additionally, absorption
in the plena cause deviation of the thermal flux from a sinusoidal shape in the
\gls{MSRE} design case. The peak power density from the \gls{MSRE} calculation
is 31 kW/L; the corresponding value for Moltres is 29 kW/L.

@@

Although the qualitative agreement is decent, there are discrepancies between
the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
the hottest channel. The peak graphite temperature is around 14 K larger in the
Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
roughly 20\%. These are not insignificant differences. However, given the
differing nature of the two models--no axial conduction in the \gls{MSRE} model,
2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
Moltres calculation--we believe this variation in quantitative behavior is
acceptable for the purpose of this work, which is to introduce Moltres as a
simulation tool. One additional feature that could influence Moltres results is
inclusion of precursor decay heat; this is under active development. Trustworthy
verification of Moltres results, such as spatial flux and temperature profiles,
will require more detailed experimental measurements than those available in the
\gls{ORNL} technical reports, which contain only macroscopic data such as
steady-state power and heat-exchanger temperature drops. Additionally, detailed
comparison with other modern modeling efforts such as that conducted in
\cite{aufiero_development_2014,laureau_transient_2017} is desirable. In that
vein, a collaboration is under way with the primary author of
\cite{aufiero_develoment_2014} to try and reproduce calculation results from
OpenFOAM. We hope to publish the results of this comparison in a future work.

### 2017-11-27 revise/revise.tex
Describe peak power density.
Add additional sentence about precursor decay heat.

\question Is the heat generation in the hottest channel the same for the Moltres and the MSRE model?
\begin{solution}
        <++>
\end{solution}

@@

        Although the qualitative agreement is decent, there are discrepancies between
        the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
        offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
        the hottest channel. The peak graphite temperature is around 14 K larger in the
        Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
        roughly 20\%. These are not insignificant differences. However, given the
        differing nature of the two models--no axial conduction in the \gls{MSRE} model,
        2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
        Moltres calculation--we believe this variation in quantitative behavior is
        acceptable for the purpose of this work, which is to introduce Moltres as a
        simulation tool. Trustworthy verification of Moltres results, such as spatial flux
        and temperature profiles, will require more detailed experimental measurements
        than those available in the \gls{ORNL} technical reports, which contain only
        macroscopic data such as steady-state power and heat-exchanger temperature
        drops. Additionally, detailed comparison with other modern modeling efforts such
        as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
        desirable. In that vein, a collaboration is under way with the primary author of
        \cite{aufiero_develoment_2014} to try and reproduce calculation results from
        OpenFOAM. We hope to publish the results of this comparison in a future work.
\end{solution}

>>>>

\question Is the heat generation in the hottest channel the same for the Moltres and the MSRE model?
\begin{solution}
        The peak power density for the MSRE model is 31 kW/L; for Moltres it is
        29 kW/L. A corresponding line has been added to the manuscript.
\end{solution}

@@

        Although the qualitative agreement is decent, there are discrepancies
        between the \gls{MSRE} and Moltres calculations. As outlined above there
        is an 11 K offset between \gls{MSRE} and Moltres calculations for the
        fuel temperature in the hottest channel. The peak graphite temperature
        is around 14 K larger in the Moltres calculation. Fast fluxes are larger
        in the \gls{MSRE} calculation by roughly 20\%. These are not
        insignificant differences. However, given the differing nature of the
        two models--no axial conduction in the \gls{MSRE} model, 2-group vs
        32-group neutronics, exclusion of the control rod thimbles in the
        Moltres calculation--we believe this variation in quantitative behavior
        is acceptable for the purpose of this work, which is to introduce
        Moltres as a simulation tool. One additional feature that could
        influence Moltres results is inclusion of precursor decay heat; this is
        under active development. Trustworthy verification of Moltres results,
        such as spatial flux and temperature profiles, will require more
        detailed experimental measurements than those available in the
        \gls{ORNL} technical reports, which contain only macroscopic data such
        as steady-state power and heat-exchanger temperature
        drops. Additionally, detailed comparison with other modern modeling
        efforts such as that conducted in
        \cite{aufiero_development_2014,laureau_transient_2017} is desirable. In
        that vein, a collaboration is under way with the primary author of
        \cite{aufiero_develoment_2014} to try and reproduce calculation results
        from OpenFOAM. We hope to publish the results of this comparison in a
        future work.
\end{solution}
